Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-02-04 paper.tex
Item 37: Regraphed figure 11 to have proper number of decimal places on axes
Item 20: Amended used of 0.1X before explaining its meaning

Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
A 0.1X concentration solution of Phosphate Buffered Saline (PBS) is common in the case of Spinal Cord Stimulators (SCS), while 1.0X PBS is considered more representative of the situation in blood.
In this manuscript we report how the parameters of the non-linear model change as the concentration of saline is varied. We place these parameters in context with a biological measurement made in the spinal cavity of a live sheep.

@@

\begin{figure}
    \begin{center}
        \includegraphics{graphics/faradaic_currentVsTime_IEEE}
    \end{center}
    \caption{Current versus time for 1.0X PBS overlaid with simulated results of the interface model's response to increasing voltage steps. The model used for simulation includes the CPE, diodes and $R_{S}$.}
    \label{fig:faradaic_currentVsTime}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/faradaic_currentVsVoltage_IEEE}
    \end{center}
    \caption{Simulated response of the interface model compared to measurement from the electrodes with a stepped voltage overpotential. Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
    \label{fig:faradaic_currentVsVoltage}
\end{figure}

@@

1. P1, top RH col. ``0.1X'' ought to be explained when you first use this form.\\
{\color{OliveGreen}
    Item 20\\
    {\color{Red} Replace ``A 0.1X concentration'' with ``a one-tenth concentration...'' and explain exactly what that means.}
    No response yet.
}\\

>>>>

Electrodes in the laboratory are typically tested in a saline solution selected to mimic the circumstances in which they will operate when implanted.
A solution of Phosphate Buffered Saline (PBS) diluted to one-tenth concentration (0.1X) is common in the case of Spinal Cord Stimulators (SCS), while full concentration (1.0X) PBS is considered more representative of the situation in blood.
In this manuscript we report how the parameters of the non-linear model change as the concentration of saline is varied. We place these parameters in context with a biological measurement made in the spinal cavity of a live sheep.

@@

\begin{figure}
    \begin{center}
        \includegraphics{graphics/faradaic_currentVsTimeIEEE}
    \end{center}
    \caption{Current versus time for 1.0X PBS overlaid with simulated results of the interface model's response to increasing voltage steps. The model used for simulation includes the CPE, diodes and $R_{S}$.}
    \label{fig:faradaic_currentVsTime}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/faradaic_currentVsVoltageIEEE}
    \end{center}
    \caption{Simulated response of the interface model compared to measurement from the electrodes with a stepped voltage overpotential. Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
    \label{fig:faradaic_currentVsVoltage}
\end{figure}

@@

1. P1, top RH col. ``0.1X'' ought to be explained when you first use this form.\\
{\color{OliveGreen}
    Item 20\\
    {\color{Red} Replace ``A 0.1X concentration'' with ``a one-tenth concentration...'' and explain exactly what that means.}
    Yes, thank you, see amendment.
}\\
